Efficient Coalition Formation \\ for Web Services

### 2013-06-12 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@

We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}. The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community. The first table in figure \ref{example_1} lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their $Th_{ws}$ throughput value. The second table shows all the possible communities and their worth. The values suggest, communities having more web services have better gain and output. However community tries to distribute the gain between web services. Sometimes it is impossible to share the gain between all web services in a way no subset of them would individually gain more if they had their own group. In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, with ${ws_3}$ joining the community the value of community increases to 8.0, however there is no way to distribute the value among web services, where ${ws_1}$ and ${ws_2}$ can earn 7.2, and ${ws_3}$ earn at least 2.4, which they could earn before joining the community. This makes the group unstable. In the example of table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the the value of cumminity. The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community. In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.

Now we consider another example, in which we have different comunitites with different market share and ${R_C}$ values, and also web services having a small share of market share independantly, providing them with a small task pull. In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$. In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yeilds a total value of $32 + 16 = 48$. In these type of scenarios,

@@

@@

In this scenario, we assume the existence of a typical community
managed by its master, and web services need to join it to be able
to get requests from the master. The community master is
characterized by a requests rate $(R_{M})$ from users. Each web
service comes with a given QoS ($QoS_{ws}$) from which the
throughput $T_{ws}$ is excluded. This exclusion allows us to build
our analysis on the particular value of $T_{ws}$. Throughput is
the average rate of tasks a web service can perform per time unit.
Thus, web services perform tasks with an average output quality of
$QoS_{ws}$ and a throughput rate of $T_{ws}$. In this setting, we
define the value of the coalition of the web services within a
community as a function increasing in both $T_{ws}$ and $QoS_{ws}$
as follows:
\begin{equation*}
output(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
\end{equation*}
\setlength{\abovedisplayshortskip}{2pt}
\begin{equation}
v(C) = \left\{
  \begin{array}{l l}
    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{M}$}\\
    output(C) \times \frac{R_{M}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{M}$}
  \end{array} \right.
\end{equation}

@@

\subsection {Web Services Collaborating Independently}

In this scenario, there is no pre-defined community and web
services are interested in forming new ones to perform better and
share benefits (see Figure \ref{fig_sim3}). Consequently, there is
no master web service providing requests for others, but each web
service comes with its own request load called \emph{market
share}. Communities can be formed because by working together web
services can expect to gain more than working individually. The
worth or value of a coalition of web services is different in this
setting. Let $metrics$ be the set of quality metrics, we average
the values $Q^m_{ws}$ for all quality metrics ($m \in metrics$)
for each web service $ws$, multiply it by a weight reflecting the
importance of each metric for each web service ($w^m_{ws}$) (Note
that $ \sum_{m}{w^m_{ws}} = 1 $). For each web service, we
multiply this weighted average by web service's market share
$(\mu_{ws})$ and the summation over all the web services of the
community to be established would be the characteristic or
valuation function. This function has the property to be
increasing in the market share and QoS.

\begin{equation}
v(C) = \sum_{ws \in C}{ \Big( \frac{\sum_{m \in metrics}{Q^m_{ws}
\times w^m_{ws}}}{|metrics|} \Big) \times \mu_{ws} }
\end{equation}

%$CC^{m}$ is \emph{Collabrative Coefficient} for each QoS metric (non-functional parameter), it determines how web services providing that QoS metric individually will be effected in a coalition environment. If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone.
As there is no pre-defined master web services in this scenario,
we assume that the members of each coalition either dynamically
vote for one, or collaborate and distribute tasks in round robin
or fair fashion. To form stable coalitions, we use the same
merge-and-split algorithm we applied for the \emph{``Web Services
and Many Communities''} scenario.

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{s3.eps}
\caption{Web Services collaborating independently}
\label{fig_sim3}
\end{figure}

>>>>

While distributing tasks, the community master can verify the performance, throughput and quality of tasks being performed by web services. It can recognize if web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in quality metrics or throughput, the master community will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations and also penalize them. Therefor its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it's important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}. The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community. The first table in figure \ref{example_1} lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their $Th_{ws}$ throughput value. The second table shows all the possible communities and their worth. The values suggest, communities having more web services have better gain and output. However community tries to distribute the gain between web services. Sometimes it is impossible to share the gain between all web services in a way no subset of them would individually gain more if they had their own group. In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, with ${ws_3}$ joining the community the value of community increases to 8.0, however there is no way to distribute the value among web services, where ${ws_1}$ and ${ws_2}$ can earn 7.2, and ${ws_3}$ earn at least 2.4, which they could earn before joining the community. This makes the group unstable. In the example of table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the value of community. The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community. In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.

@@

Now we consider another example, in which we have different communities with different market share, ${R_C}$ values. Web services also have a small share of market independently, providing them with a small task pull. In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$. In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$. In these types of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition. The communities usually start the game having some established members, encountering new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant. In this example if we initially having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_1}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_2}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.

@@

In this scenario, we assume the existence of a typical community
managed by its master, and web services need to join it to be able
to get requests from the master. The community master is
characterized by a requests rate $(R_{C})$ from users. Each web
service comes with a given QoS ($QoS_{ws}$) from which the
throughput $T_{ws}$ is excluded. This exclusion allows us to build
our analysis on the particular value of $T_{ws}$. Throughput is
the average rate of tasks a web service can perform per time unit.
Thus, web services perform tasks with an average output quality of
$QoS_{ws}$ and a throughput rate of $T_{ws}$. In this setting, we
define the value of the coalition of the web services within a
community as a function increasing in both $T_{ws}$ and $QoS_{ws}$
as follows:
\begin{equation*}
output(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
\end{equation*}
\setlength{\abovedisplayshortskip}{2pt}
\begin{equation}\label{eq:valuation}
v(C) = \left\{
  \begin{array}{l l}
    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{C}$}\\
    output(C) \times \frac{R_{C}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{C}$}
  \end{array} \right.
\end{equation}

@@

\subsection{Taxtation and Community Stability}\label{s:tax}

We discuessed $core$ as one the preeminent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept opening room for agents to cooperate and stay in the community and increasing the community stability. The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent point of view. It claims agents for any reason will be not willing to deviate to gain less that $\epsilon$ amount of profit. However, in our case, the community master is willing to keep web services in communities too. There are several reasons for this, one is there is always possibility that agents may leave the community or they may under perform from the values they initially performing with. According to the web service community's valuation function \ref{eq:valuation} and as mentioned in examples 1, 2 and 3,
